---
title: "2020 Media Coverage"
author: "Hoda Abdalla"
date: "10/1/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(readxl)
```

```{r}
x <- read_csv(file = "https://raw.githubusercontent.com/fivethirtyeight/data/master/media-mentions-2020/cable_weekly.csv", 
              col_types = cols(
  date = col_date(format = ""),
  name = col_character(),
  matched_clips = col_double(),
  all_candidate_clips = col_double(),
  total_clips = col_double(),
  pct_of_all_candidate_clips = col_double(),
  query = col_character()
))

y <- read_csv(file = "https://raw.githubusercontent.com/fivethirtyeight/data/master/media-mentions-2020/online_weekly.csv",
              col_types = cols(
  date = col_date(format = ""),
  name = col_character(),
  matched_stories = col_double(),
  all_candidate_stories = col_double(),
  pct_of_all_candidate_stories = col_double(),
  query = col_character()
))
```
My current plan is to examine media coverage of 2020 presidential candidates and compare the media coverage with polling data. I got the cable news and online media mention data from fivethirtyeight. I do not currently have polling data, but I am looking to use the data from the New York Times, which also includes individual campaign contribution numbers. I only want to look at the top 10 candidates in each respect.
